14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-19 rules/rules19.tex
Rules: More in tracks.

\header{Input/Output.}
This track will consist of selected non-incremental benchmarks in each of
the logic divisions.  Each benchmark will be presented to the solver as its
first command-line argument.  The solver is then expected to report on its
standard output channel whether the formula is satisfiable (\texttt{sat}) or
unsatisfiable (\texttt{unsat}).  A solver may also report \texttt{unknown} to
indicate that it cannot determine satisfiability of the formula.

@@

@@

The \challtrack will include both non-incremental and incremental benchmarks and
it will follow the same rules as the \inctrack and  \maintrack, respectively
with two exceptions: benchmark selection and the time limit. The track will
run on challenging industrial benchmarks provided by the community. This year,
the \challtrack will include both incremental and single query benchmarks in the
following logics QF\_BV, QF\_ABV and QF\_AUFBV. The complete list of benchmarks
along with instructions on how to access them will be provided on the SMT-COMP
website as soon as the benchmarks are released.

@@

@@

\header{Benchmark selection.} \label{benchmark-selection}
%
The competition will use a large subset of SMT-LIB benchmarks, with some
guarantees on including new benchmarks.  In all tracks the following
process will be used for culling the benchmark pool.
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The competition
  organizers may remove benchmarks that are deemed inappropriate or
  uninteresting for competition, or cut the size of certain benchmark
  families to avoid their over-representation.  SMT-COMP attempts to
  give preference to benchmarks that are ``real-world,'' in the sense
  of coming from or having some intended application outside SMT.
\item \emph{Remove easy benchmarks.} The competition organizers will
    remove all benchmarks that were solved by all solvers (including the
        non-competitive solvers) in less than one second in the 2018 SMT
        competition.
\item \emph{Cap the number of instances in a division.} The competition
  organizers will limit the number of benchmarks in a division as
  follows:
  \begin{enumerate}
  \item If a division contains less than 300 instances, all
        the instances will selected.
  \item If a division contains between 300 and 600 instances,
        a selection of 300 instances from the set will be selected.
  \item If a division contains more than 600 instances, 50\% of
        the benchmarks will be selected.
  \end{enumerate}
\item \emph{\ucoretrack{}.} In addition, for the \ucoretrack{}, all
  benchmarks with a single assertion will be removed.
\end{enumerate}
%
The selection process in cases (b) and (c) above will guarantee the
inclusion of new benchmarks by first picking randomly one benchmark from
each new benchmark family.  The rest of the benchmarks will be chosen
randomly from the remaining benchmarks using a uniform distribution.
%
The culling script will be publicly available and will use the same
random seed as the rest of the competition.  The set of benchmarks
selected for the competition will be published when the competition
begins.

>>>>

The \maintrack track will consist of selected non-incremental benchmarks in
each of the competitive logic divisions.  Each benchmark will be presented to
the solver as its first command-line argument.  The solver is then expected to
report on its standard output channel whether the formula is satisfiable
(\texttt{sat}) or unsatisfiable (\texttt{unsat}).  A solver may also report
\texttt{unknown} to indicate that it cannot determine satisfiability of the
formula.

\header{Benchmark Selection.} See page~\pageref{benchmark-selection}.

@@

\header{Post-Processor.}
This track uses the post-processor at \rem{link tba} to accumulate the results.

@@

The \challtrack will include both non-incremental and incremental benchmarks.
It will follow the same rules as the \maintrack and \inctrack, respectively,
with two exceptions: benchmark selection and the time limit.

\header{Benchmark Selection.}
This track will run on challenging industrial benchmarks provided by the
community. This year, the \challtrack will include the complete set of provided
benchmarks dedicated to this track, which consist of both incremental and
single query benchmarks in the logics QF\_BV, QF\_ABV and QF\_AUFBV. The
complete list of benchmarks along with instructions on how to access them will
be provided on the SMT-COMP website as soon as the benchmark library is
released.

@@

\header{Post-Processor.}
This track uses the post-processors from the \maintrack (for non-incremental
benchmarks) and the \inctrack (for incremental benchmarks) to accumulate the
results.

@@

\header{Benchmark selection.} \label{benchmark-selection}
%
The competition will use a large subset of SMT-LIB benchmarks, with some
guarantees on including new benchmarks.  In \textbf{all} tracks \textbf{except}
the \challtrack, the following selection process will be used.
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The competition
  organizers may remove benchmarks that are deemed inappropriate or
  uninteresting for competition, or cut the size of certain benchmark
  families to avoid their over-representation.  SMT-COMP attempts to
  give preference to benchmarks that are ``real-world,'' in the sense
  of coming from or having some intended application outside SMT.
\item \emph{Remove easy benchmarks.} The competition organizers will
    remove all benchmarks that were solved by all solvers (including the
        non-competitive solvers) in less than one second in the 2018 SMT
        competition.
\item \emph{Cap the number of instances in a division.} The competition
  organizers will limit the number of benchmarks in a division as
  follows:
  \begin{enumerate}
  \item If a division contains less than 300 instances, all
        the instances will selected.
  \item If a division contains between 300 and 600 instances,
        a selection of 300 instances from the set will be selected.
  \item If a division contains more than 600 instances, 50\% of
        the benchmarks will be selected.
  \end{enumerate}
\item \emph{\ucoretrack{}.} In addition, for the \ucoretrack{}, all
  benchmarks with a single assertion will be removed.
\end{enumerate}
%
The selection process in cases (b) and (c) above will guarantee the
inclusion of new benchmarks by first picking randomly one benchmark from
each new benchmark family.  The rest of the benchmarks will be chosen
randomly from the remaining benchmarks using a uniform distribution.
%
The culling script will be publicly available and will use the same
random seed as the rest of the competition.  The set of benchmarks
selected for the competition will be published when the competition
begins.
